---
name: Robert
surname: Wiederstein
position: "Programmer | Data Analyst"
address: "214 Sycamore St. Unit 402, Evansville, IN 47708"
phone: 270.869.5112
www: robwiederstein.org
email: "rob@robwiederstein.org"
twitter: RobWiederstein
github: RobWiederstein
linkedin: RobWiederstein
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
headcolor: 3026ef
profilepic: pic.jpg
csl: numeric-apa-cv.csl
docname: CV/Resume
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(glue)
library(myCV)
```

# Summary

I have been programming in R part-time for 5 years, and full time for the last two years.  My experience and interests may be quickly understood through review of my [blog](https://www.robwiederstein.org) and GitHub [account](https://github.com/RobWiederstein). My future programming goals involve optimizing applications and incorporating `C++` in my packages and building apis.



```{r load-data, include=FALSE}
jobs <- readr::read_csv("../data/jobs.csv")
schools <- readr::read_csv("../data/schools.csv")
skills <- readr::read_csv("../data/skills.csv")
```

# Education

```{r education, echo=FALSE}
detailed_entries(schools, 
                 when = glue("{start_date}--{end_date}"),
                 what = degree,
                 where = loc,
                 with = uni)
```

# Work

```{r work}
jobs %>% 
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    with = company,
    where = where,
    why = details)
```
# Publications

```{r Publications}
bibliography_entries("pubs.bib")
```

# Selected Presentations

```{r Presentations}
# Normal articles excluding editorials
bibliography_entries("talks.bib")
```

# Skills

```{r skills}
skills %>%
    vitae::detailed_entries(
        with = familiar,
        what = skills
    )
```


# Packages Used

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble", "glue", "myCV"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

